---
title: "Slide Presentation"
author: "Guan Xuyi"
date: "March 15, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

##Data 
The following is the data that is used in analysis.
Both the data files are loaded to this tab in oder to analyze them to gether and do comparison

```{r}
data<-read.csv(file = "E:/AIR.TEMPERATURES.csv", header = TRUE)
data0<-read.csv(file = "E:/AIR.TEMPERATURES.csv", header = TRUE)
```
The data file for Air Temperatures is named data and that for Sea Temperatures is named data0

## Exploring Data

The r command summary() will be used to explore the data.
This gives out the following outputs:

## Exploring Air Temperatures
```{r}
summary(data)
```

##Exploring Sea Temperatures
```{r}
summary(data0)
```


## ploting the data for Air Temperatures
```{r}
plot<-ggplot(data = Sea.temp, mapping = aes(TIME, AVG ), environment = parent.frame())
plot + geom_boxplot(mapping = aes(TIME))
```

## Plotting data for Sea temperatures
```{r}
plot0<-ggplot(data = Sea.temp, mapping = aes(TIME, AVG ), environment = parent.frame())
plot0 + geom_boxplot(mapping = aes(TIME))
```



