---
title: "Slide Presentation"
author: "Guan Xuyi, Deyan Hao"
date: "March 15, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```
## Introduction
In this project, we will 

1. read, clean, and organize the data from the website for NOAA Weather Station buoy 46035 at 57.026 N 177.738 W in the NOAA National Data Buoy Center 

2. produce a time series composed of 30 years of daily Air Temperature and Sea Temperature readings recorded at noon

3. visualize and explore the correlation between air temperature and sea temperature 

4. test whether the mean temperature changed over the past 30 years

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(stringr)

a <- "http://www.ndbc.noaa.gov/view_text_file.php?filename=46035h"
b <- ".txt.gz&dir=data/historical/stdmet/"
years <- c(1988:2017)

years <- years[-26]
urls <- str_c(a, years, b, sep = "")
filenames <- str_c("mr", years, sep = "")

N <- length(urls)


for (i in 1:N){
  suppressMessages(assign(filenames[i], read_table(urls[i], col_names = TRUE)))
  file <- get(filenames[i])
  colnames(file)[1] <-"YYYY"
  if (i < 18) {
    file <- file %>% mutate(mm = "00")
  }
  file <- file %>% select(YYYY, MM, DD, hh, mm, ATMP, WTMP)
  if (i >= 20) {
    file <- file[-1,]
  }
  if (i >= 26) {
    file[1] <- i + 1988
  }
  else{
    file[1] <- i + 1987
  }
  if(i == 1){
    total <- file
  }
  else{
    total <- rbind.data.frame(total, file)
  }
}

 
noon <- total %>% filter((hh == "11" & mm == "50") | (hh == "12" & mm == "00"))


noon$ATMP <- as.numeric(noon$ATMP)
noon$WTMP <- as.numeric(noon$WTMP)


noon$ATMP <- ifelse(noon$ATMP > 90, NA, noon$ATMP)
noon$WTMP <- ifelse(noon$WTMP > 90, NA, noon$WTMP)


noon <- unite(noon, Date, YYYY, MM, DD, sep = "-")
noon$Date <-as.Date(noon$Date)

```

## Time Series for Air Temperature
```{r echo=FALSE, message=FALSE, warning=FALSE}
noon %>% ggplot(aes(Date, ATMP)) +
  geom_line(na.rm = TRUE, col = "red") +
  labs(title = "Time Series of Air Temperature (noon)",
       subtitle = "Data obtained from the National Data Buoy Center",
       y = "Temperature (Celcius)",
       x = "Year")

```

## Time Series for Sea Temperature
```{r echo=FALSE, message=FALSE, warning=FALSE}
noon %>% ggplot(aes(Date, WTMP)) +
  geom_line(na.rm = TRUE, col = "blue") +
  labs(title = "Time Series of Sea Temperature (noon)",
       subtitle = "Data obtained from the National Data Buoy Center",
       y = "Temperature (Celcius)",
       x = "Year")
```

## Time Series for Air and Sea Temperatures
```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(noon, aes(Date)) + 
  geom_line(aes(y = ATMP, col = "ATMP")) + 
  geom_line(aes(y = WTMP, col = "WTMP")) +
  scale_colour_manual(values=c("red", "blue")) +
  labs(x = "Year", y = "Temperature (Celcius Degree)",
       title = "Time Series of Air & Sea Temperature (Noon Data)",
       subtitle = "Data obtained from the National Data Buoy Center")
```

## Scatter Plot to See the Correlation between ATMP and WTMP
```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(noon) + 
  geom_point(mapping = aes(x = ATMP, y = WTMP)) +
  labs(x = "Noon Air Temp (Celcius)", 
       y = "Noon Sea Temp (Celcius)",
       title = "Scatter Plot to See the Correlation between ATMP and WTMP")

```

##  Smooth Line to See the Correlation between ATMP and WTMP
```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(noon) + 
  geom_smooth(mapping = aes(x = ATMP, y = WTMP)) +
  labs(x = "Noon Air Temp (Celcius)", 
       y = "Noon Sea Temp (Celcius)",
       title = "Smooth Line to See the Correlation between ATMP and WTMP")

```

## Air and Sea Temperature Correlation
```{r echo=FALSE, message=FALSE, warning=FALSE}
cor.test(noon$ATMP, noon$WTMP, method = "pearson")
```

## Test Whether Air Temperature Changed from 1988 to 2017 (Noon Data)
```{r warning=FALSE, include=FALSE}
x <- noon %>% separate(Date, into = c("YYYY", "MM", "DD"), sep = "-") %>% 
  filter(YYYY == 1988)
y <- noon %>% separate(Date, into = c("YYYY", "MM", "DD"), sep = "-") %>% 
  filter(YYYY == 2017)

t.test(x$ATMP, y$ATMP)
```
Because the p-value = 5.153e-13 < 0.01, we reject the null hypothesis that the means of ATMP in 1988 and in 2017 are equal, so the air temp changed over 30 years.
Means in two years:2.330748  4.645179 

## Test Whether Sea Temperature Changed from 1988 to 2017 (Noon Data)
```{r warning=FALSE, include=FALSE}
t.test(x$WTMP, y$WTMP)
```
Because the p-value = 9.035e-13 < 0.01, we reject the null hypothesis that the means of WTMP in 1988 and in 2017 are equal,so the sea temp changed over 30 years.
Means in two years: 4.572981  6.141525 

## Test Whether Air Temperature Changed from 1988 to 2017 (Total Data)
```{r warning=FALSE, include=FALSE}
mr1988 <- mr1988 %>% mutate(ATMP = ifelse(ATMP > 90, NA, ATMP)) %>% 
  mutate(ATMP = as.numeric(ATMP))
mr2017 <- mr2017 %>% mutate(ATMP = ifelse(ATMP > 90, NA, ATMP)) %>% 
  mutate(ATMP = as.numeric(ATMP))

x1 <- mr1988$ATMP
y1 <- mr2017$ATMP

t.test(x1, y1, na.rm=TRUE)
```
Because the p-value < 2.2e-16 < 0.01, we reject the null hypothesis that the means of ATMP in 1988 and in 2017 are equal,so air temp changed over 30 years.
Means in two years:  2.438602  4.714333

## Test Whether Sea Temperature Changed from 1988 to 2017 (Total Data)
```{r message=FALSE, warning=FALSE, include=FALSE}
mr1988 <- mr1988 %>% mutate(WTMP = ifelse(WTMP > 90, NA, WTMP)) %>% 
  mutate(WTMP = as.numeric(WTMP))
mr2017 <- mr2017 %>% mutate(WTMP = ifelse(WTMP > 90, NA, WTMP)) %>% 
  mutate(WTMP = as.numeric(WTMP))

x2 <- mr1988$WTMP
y2 <- mr2017$WTMP

t.test(x2, y2, na.rm=TRUE)
```
Because the p-value < 2.2e-16 < 0.01, we reject the null hypothesis that the means of WTMP in 1988 and in 2017 are equal,so sea temp changed over 30 years.
Means in two years:  4.608660  6.156853
