---
title: "Slide presentation"
author: "Guan Xuyi"
date: "March 15, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
data<-read.csv(file = "E:/veg1.csv", header = TRUE)
```

## Description of the data

<br>
</center>

- This data was created with USDA quickstats system using the following parameters:
1. Program: Survey
2. Sector: Environmental
3. Group: Vegetables
4. Commodity: Vegetables Totals, Vegetables other, Broccoli, Brussels Sprouts, Cauliflower.
- All the other parameters in the data were left open
- The data was collected to gain insights about chemical treatments applied to food crops e.g. fertilizers, insecticides, etc.
- This findings will be presented in a ggplot and a shiny dashboard.

## Reference material
<br>
 [tidyverse](https://www.tidyverse.org/) 

 [ggplot2](http://ggplot2.org/)
[cheatsheet - ggplot2](https://www.rstudio.com/wp-content/uploads/2015/03/ggplot2-cheatsheet.pdf)

 [dplyr](https://stackoverflow.com/tags/dplyr/info)  

 [Pandoc](http://pandoc.org/index.html)  



## Summary Output Slide
```{r echo=FALSE}
summary(data)
```

##GGplot slide
 
 I will use the veg.1 dataset.
 
 This gives an empty graph.
 
* Add layers to it with GEOM_FUNCTIONS.  

* [List of GEOMs](http://bit.ly/2Em0BsV) 

* Each geom takes mapping argument which uses aes() to map the x and y axes.  

* Add additional dimensions by mapping with color, shapes, size to other variables 

```{r echo=FALSE, message=FALSE}
library(tidyverse)

```


## Slide with R Output




